Notes on Control Plane Inference

### 2021-05-28 inference.tex
close holes in proofs

% sets
\newcommand{\Value}{\mathsf{Value}}
\newcommand{\BVExpr}{\mathsf{BVExpr}}
\newcommand{\BExpr}{\mathsf{BExpr}}
\newcommand{\Cmd}{\mathsf{Cmd}}
\newcommand{\Action}{\mathsf{Action}}
\newcommand{\Instr}{\mathsf{Instr}}
\newcommand{\Prog}{\mathsf{Prog}}
\newcommand{\GCL}{\mathsf{GCL}}
\newcommand{\Pkt}{\mathsf{Pkt}}
\newcommand{\Model}{\mathsf{Model}}
\newcommand{\Hdr}{\mathsf{Hdr}}
\newcommand{\Field}{\mathsf{Field}}
\newcommand{\Table}{\mathsf{Table}}
\newcommand{\Row}{\mathsf{Row}}
\newcommand{\List}{\mathsf{List}}
\newcommand{\Var}{\mathsf{Var}}
\newcommand{\SymbRow}{\mathsf{SymbRow}}
\newcommand{\State}{\mathsf{State}}
\newcommand{\Kind}{\mathsf{Kind}}

@@

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}

@@

\paragraph{Packets}
Our dataplane programs will reason about structured representations of packets,
that is, they will be transformations on sets of packet headers. In P4 programs,
packet headers $h \in \Hdr$ are essentially structs with fields $f \in \Field$.
Write $h.f$ for a header $h$ and a field $f$ is the value $v$ of $f$ in header
$h$. Our simple command language just treats ``h.f'' as a variable.

@@

\paragraph{Symbolic Table Rows}
A symbolic table row $\rho \in \SymbRow$ represents a symbolic row. These rows are represented in our programs as simple variables $x$. Like tables,
rows are also records with the following fields \todo{Well formedness constraint?}
\begin{enumerate}[align=left]
  \item[($\rho.\matches$)] A list variable of length representing the possible match keys.
  \item[($\rho.\action$)] A variable representing the action choice
  \item[($\rho.\data$)] A list variable representing the possible action data
\end{enumerate}

@@

\paragraph{Values}
Values $v \in \BVExpr$ are bitvector literals, written $[n]_w$, where $n$
is a natural value and $w$ is the width. We say that $[n]_w = [m]_l$ is
undefined if $w \neq l$, and otherwise is true iff $n \equiv m \mod 2^w$.

@@

\paragraph{Commands}
Data plane programs $c \in \mathsf{Cmd}$ can be assignments ($h.f := e$), havoc statements ($\havoc x$),
assumptions ($\assume b$), assertions ($\assert b$), table application
($t.\apply()$), sequential composition ($c_1;c_2$ for two commands $c_1$ and $c_2$), and
nondeterministic choice ($c_1 \choice c_2$ for two commands $c_1$ and $c_2$).

@@

\paragraph{Packets}
A packet $\pkt$ is a map from header fields to values. Use the syntax $\pkt[x
  \mapsto v]$ to represent the packet that is equivalent to $\pkt$ on all variables
fields except $x$, which maps to $v$.

\paragraph{State}
On-switch state is represented by a mapping from tables identifiers $t.\id$ to
lists of rows $[r_1,\ldots,r_n] \in \Row(t)^*$.

A similar to a symbolic row $\rho$, a concrete row $r$ comprises a list of match
values $r.\matches$, an action identifier $r.\action$, and a list of action data
$r.\data$. A concrete row $r$ is in the set $\Row(t)$ if it is well formed for a
table $t$ iff the following conditions hold:
\begin{enumerate}
\item $|r.\matches| = |t.\keys|$
\item $r.\action < |t.\actions|$
\item $|r.\data| = |\vec x|$ where $\lambda \vec x. c = t.\actions[r.\action]$
\end{enumerate}\

A state map $\sigma : \Value \to \Row^*$ is well-formed for a command $c$ iff the
following conditions hold:
\begin{enumerate}[align=left]
\item[(\textsc{Total})] For every $t \in \tables(c)$ $\pkt \in \pkt$ there exists a row $r \in \sigma(t.\id)$ such that $r.matches = \pkt(t.keys)$.
\item[(\textsc{WellFormedRows})] For every $t\in \tables(c)$, every row in $\sigma(t.\id)$ is well-formed.
\item[(\textsc{NoShadow})] For every $t \in \tables(c)$, with $r_1,\ldots,r_n =
  \sigma(t.\id)$, for every $1 \leq i \leq n$, there does not exist $1 \leq j <
  i$ such that $r_i.\matches = r_j.\matches$.
\end{enumerate}

Importantly, we assume that all state is \emph{total}, that is, no packet locally misses
in the table. This is formally defined in Definition~\ref{def:total-state}.

%% \begin{definition}[Total State]
%%   \label{def:total-state}
%%   A state $\sigma$ is total if for every $t \in \dom(\sigma)$, the following
%%   formula is valid:
%%   \[\bigvee_{r \in \sigma(t.\id)} t.\keys = r.\matches \]
%% \end{definition}

%% Henceforth we assume that all states are total.

%% \todo[inline]{Can be Removed(?)}

@@

\begin{definition}[Variables]
  The free variables of a command $c$, written $\fvs(c) \subseteq \Var$, is the
  set of variables that occur at any point in $c$ (i.e. as the lhs of an
  assignment, in a boolean expression, a bitvector expression, as a key in a
  table.) The only bound variables are the action data in tables. Formally:
  \[\begin{array}{l >{\triangleq}cl}
  \efvs :: \BVExpr \to \mathcal{P}(\Var) \\
  \efvs(v) && \{\} \\
  \efvs(x) && \{x\}\\
  \efvs(e_1 \binop e_2) && \efvs(e_1) \cup \efvs(e_2)\\
  \efvs(\unop e) && \efvs(unop) \\[1em]
  \bfvs :: \BExpr \to \mathcal{P}(\Var) \\
  \bfvs(\FALSE) && \{\}\\
  \bfvs(b_1 \Rightarrow b_2) && \bfvs(b_1) \cup \bfvs(b_2)\\
  \bfvs(e_1 = e_2) && \efvs(e_1) = \efvs(e_2) \\[1em]
  \fvs :: \Cmd \to \mathcal{P}(\Var) \\
  \fvs(x := e) && \{x\} \cup \fvs(e)\\
  \fvs(\havoc x) && \{x\}\\
  \fvs(\assume b) && \fvs(b)\\
  \fvs(\assert b) && \fvs(b) \\
  \fvs(c_1;c_2) && \fvs(c_1) \cup \fvs(c_1) \\
  \fvs(c_1 \choice c_2) && \fvs(c_1) \cup \fvs(c_2) \\
  \fvs(t.\apply()) &&
  t.\keys \cup \bigcup_{\lambda \vec x. c \in t.\actions} (\fvs(c) \setminus \{x_1,\ldots, x_n\})
  \end{array}\]
\end{definition}

@@

\begin{lemma}[Subset Implies Projected Subset]
  \label{lem:subset-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P \subseteq Q$ then $P \subseteq_V Q$.
\end{lemma}

\begin{proof}
Let $P,Q \subseteq \Pkt$ and $V \subseteq \Var$ be given. Assume $P \subseteq Q$,
to show that $P \subseteq_V Q$.

Let $\pkt \in P$. Since $P \subseteq Q$, $\pkt \in Q$. Notice that $\pkt =_V
\pkt$, so $P \subseteq_V Q$.
\end{proof}

\begin{lemma}[Equality Implies Projected Equality]
  \label{lem:equal-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P = Q$ then $P =_V Q$.
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:subset-proj}
\end{proof}

\begin{lemma}[Expression Projection]
  \label{lem:proj-expr}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  expression $e \in \BVExpr$, such that $\efvs(e) \subseteq V$, $\edenote{e}\pkt =
  \edenote{e}(\pkt|_V)$.
\end{lemma}

\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $e$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($e = v$)] Let $\pkt$ be given. $\edenote{v}\pkt = v = \edenote{v}{\pkt|_V}$
  \item[($e = x$)] Let $\pkt$ be given. Note that $\efvs(x) = \{x\} \subseteq V$. Compute:
    \[\begin{array}{ll}
    \edenote{x}(\pkt|_V) \\
    = (\pkt|_V)(x)
    & \text{by definition of }\edenote\cdot\\
    = \{y \mapsto \pkt(y) \mid y \in V\}(x)
    & \text{by definition of }(\cdot)|_V : \Pkt \to \Pkt\\
    = \pkt(x) & \text{since } x \in V
    \end{array}
    \]
  \item[($e = e_1 \binop e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{e_1 \binop e_2}\pkt \\
    = \edenote{e_1}\pkt \binop \edenote{e_2}\pkt & \text{definition of }\edenote\cdot \\
    = \edenote{e_1}(\pkt|_V) \binop \edenote{e_2}(\pkt|_V) & \text{by IHS since }\efvs(e_i) \subseteq \efvs(e_1 \binop e_2) \subseteq V, i = 1,2 \\
    = \edenote{e_1 \binop e_2}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \item[($e = \unop e$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{\unop e}\pkt \\
    = \unop \edenote{e}\pkt & \text{definition of }\edenote\cdot \\
    = \unop \edenote{e}(\pkt|_V) & \text{by IH, since } \efvs(e) = \efvs(\unop e) \subseteq V \\
    = \edenote{\unop e}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \end{enumerate}
\end{proof}

@@

@@

\begin{lemma}[Pseudo-Parametricity]
  \label{lem:parametricity}
  For $c \in \Cmd$, $\sigma : \State$, $y \in \Var$, $\pkt \in \Pkt$, if $y
  \not\in \fvs(c)$, then $\forall \pkt' \in \denote{c}^\sigma \pkt$, $\pkt'(y) =
  \pkt(y)$.
\end{lemma}

@@

\begin{lemma}[Disjoint Commutativity]
  \label{lem:disj-comm}
  For $c_1,c_2 \in \Cmd$, and $\sigma \in \State$ if $\fvs(c_1) \cap
  \fvs(c_2) = \emptyset$, $ \forall \pkt \in \Pkt. \denote{c_1;c_2}^\sigma\pkt =
  \denote{c_2;c_1}^\sigma \pkt$.
\end{lemma}
\begin{proof}
  \todo[inline]{todo}
\end{proof}

@@

  \multicolumn{3}{l}{\state\sigma_c \in \BExpr} \\
  \state\sigma_c &\triangleq
  & \displaystyle\bigwedge_{ t \in \tables(c) } \state\sigma^t
  \end{array}
  \]
  \caption{Symbolic State Encoding}
  \label{fig:table-instrument}
\end{figure}

@@

\begin{proof}
  Let $\sigma : \Value \to \Row^*$ and $c_1,c_2\in \Cmd$ be given. Notice that
  $\tables(c_1;c_2) = \tables(c_1) \cup \tables(c_2)$. Compute:
  \[
  \begin{array}{l >{\displaystyle}ll}
    \state\sigma_{c_1;c_2}
    & = \bigwedge_{ t \in \tables(c_1;c_2) } \state\sigma^t \\
    & = \bigwedge_{ t \in \tables(c_1)\cup \tables(c_2) } \state\sigma^t \\
    & = \bigwedge_{t \in \tables(c_1)} \state\sigma^t \wedge \bigwedge_{t \in \tables(c_2)} \state\sigma^t \\
    & = \state\sigma_{c_1} \wedge \state\sigma_{c_2}
  \end{array}
  \]
\end{proof}

\begin{lemma}[Symbolic State distributes over Choice]
  \label{lem:sigma-distrib-choice}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1 \choice c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

\begin{proof}
  Let $\sigma : \Value \to \Row^*$ and $c_1,c_2\in \Cmd$ be given. Notice that
  $\tables(c_1 \choice c_2) = \tables(c_1) \cup \tables(c_2)$. Compute:
  \[
  \begin{array}{l >{\displaystyle}ll}
    \state\sigma_{c_1 \choice c_2}
    & = \bigwedge_{ t \in \tables(c_1 \choice c_2) } \state\sigma^t \\
    & = \bigwedge_{ t \in \tables(c_1)\cup \tables(c_2) } \state\sigma^t \\
    & = \bigwedge_{t \in \tables(c_1)} \state\sigma^t \wedge \bigwedge_{t \in \tables(c_2)} \state\sigma^t \\
    & = \state\sigma_{c_1} \wedge \state\sigma_{c_2}
  \end{array}
  \]
\end{proof}

>>>>

% sets
\newcommand{\Value}{\mathsf{Value}}
\newcommand{\BVExpr}{\mathsf{BVExpr}}
\newcommand{\BExpr}{\mathsf{BExpr}}
\newcommand{\Cmd}{\mathsf{Cmd}}
\newcommand{\Action}{\mathsf{Action}}
\newcommand{\Instr}{\mathsf{Instr}}
\newcommand{\Prog}{\mathsf{Prog}}
\newcommand{\GCL}{\mathsf{GCL}}
\newcommand{\Pkt}{\mathsf{Pkt}}
\newcommand{\Model}{\mathsf{Model}}
\newcommand{\Hdr}{\mathsf{Hdr}}
\newcommand{\Field}{\mathsf{Field}}
\newcommand{\Table}{\mathsf{Table}}
\newcommand{\Row}{\mathsf{Row}}
\newcommand{\List}{\mathsf{List}}
\newcommand{\Var}{\mathsf{Var}}
\newcommand{\SymbRow}{\mathsf{SymbRow}}
\newcommand{\Ghost}{\mathsf{Ghost}}
\newcommand{\State}{\mathsf{State}}
\newcommand{\Kind}{\mathsf{Kind}}

@@

% Theorems
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

\paragraph{Variables}
Dataplane programs use variables $x \in \Var$ to represent packet state.

\paragraph{Values}
Values $v \in \Value$ are bitvector literals, written $[n]_w$, where $n$
is a natural value and $w$ is the width. We say that $[n]_w = [m]_l$ is
undefined if $w \neq l$, and otherwise is true iff $n \equiv m \mod 2^w$.

\paragraph{Packets}
Our dataplane programs will reason about structured representations of packets,
that is, they will be transformations on sets of packet headers. We define
Packets to be functions from variables to values, that is $\Pkt = \Value^\Var$.
Use the syntax $\pkt\{x \mapsto v\}$ to represent the packet that is equivalent
to $\pkt$ on all variables fields except $x$, which maps to $v$. Use $\pkt(x)$
to look up the value of $x$ in packet $\pkt$.

@@

\paragraph{Symbolic Table Rows}
A symbolic table row $\rho_t \in \SymbRow \subseteq \Var$ represents a symbolic row for table
$t$. These rows are represented in our programs as simple variables. Like
tables, rows are also ``records'' with the following fields \todo{well formedness constraint?}
\begin{enumerate}[align=left]
  \item[($\rho_t.\matches$)] A list variable of length representing the possible match keys.
  \item[($\rho_t.\action$)] A variable representing the action choice
  \item[($\rho_t.\data$)] A list variable representing the possible action data
  \item[($\rho_t.\id$)] A single variable representing the row's index.
\end{enumerate}

@@

For a set of tables $T \subseteq \Table$, we absue set-builder notation to write the shorthand
$\{\rho_t.*| t \in T \}$ to indicate the set $\{\rho_t.f | t \in T, f \in
\{\action, \id, \matches[0], \ldots, \matches[n_t], \data[0], ldots, \data[m_t]
\}\}$ where $n_t = |t.\keys|$ and $m_t = \max\{|\vec x| \mid\lambda \vec x. c
\in t.\actions\}$

\paragraph{Ghost Variables}
A ghost varaible $\gamma_t \in \Ghost \subseteq \Var$ represents some ghost
state for table $t$. These ghost variables are represented as simple variables
in our program. They are ``records'' with the following fields
\begin{enumerate}[align=left]
\item[($\gamma_t.\miss$)] Equal to $[1]_1$ if the table packet misses in the table, and $[0]_1$ otherwise.
\item[$(\gamma_t.\keys)$] A list variable that captures the values of the keys at table-application time.
\end{enumerate}

For a set of tables $T \subseteq \Table$, we absue set-builder notation to write
the shorthand $\{\gamma_t.*| t \in T \}$ to indicate the set $\{\gamma_t.f | t \in
T, f \in \{\miss, \keys[0], \ldots, \keys[n_t]\}\}$ where $n_t = |t.\keys|$.

@@

\paragraph{Commands}
Data plane programs $c \in \mathsf{Cmd}$ can be assignments ($h.f := e$), havoc
statements ($\havoc x$), assumptions ($\assume b$), assertions ($\assert b$),
table application ($t.\apply()$), sequential composition ($c_1;c_2$ for two
commands $c_1$ and $c_2$), and nondeterministic choice ($c_1 \choice c_2$ for
two commands $c_1$ and $c_2$). Note that table application, havoc, and
nondeterministic choice are is prohibited in action bodies.

\begin{definition}
  \label{def:well-formed-command}
   A command $c \in \Cmd$ is \emph{well-formed} if tables only occur once in the
   program and each has a unique $t.\id$.
\end{definition}

@@

\paragraph{State}
On-switch state is represented by a mapping from tables identifiers $t.\id$ to
lists of rows $[r_1,\ldots,r_n] \in \Row(t)^*$. I.e. the set of states $\State =
\Value \to \Row^*$

A similar to a symbolic row $\rho$, a concrete row $r$ comprises a list of match
values $r.\matches$, an action identifier $r.\action$, a list of action data
$r.\data$, and an index $r.\id$. A concrete row $r$ is in the set $\Row(t)$ if
it is well-formed for a table $t$ iff the following conditions hold:
\begin{enumerate}
\item $|r.\matches| = |t.\keys|$
\item $r.\action < |t.\actions|$
\item $|r.\data| = |\vec x|$ where $\lambda \vec x. c = t.\actions[r.\action]$
\end{enumerate}

A state map $\sigma : \Value \to \Row^*$ is well-formed for a command $c$ iff
the following conditions hold:
\begin{enumerate}[align=left]
\item[(\textsc{WellFormedRows})] For every $t\in \tables(c)$, every row in $\sigma(t.\id)$ is well-formed.
\item[(\textsc{SelfRef})] For every $t \in tables(c)$, such that $[r_1,\ldots,
  r_n] = \sigma(t.\id)$, $r_i.\id = i$ for all $1 \leq i \leq n$.
\end{enumerate}

Because of the well-formedness assumption about commands, overload $\sigma(t)
\triangleq \sigma(t.\id)$.

@@

\begin{definition}[Free Variables]
  The free variables of a command $c$, written $\fvs(c) \subseteq \Var$, is the
  set of variables that occur at any point in $c$ (i.e. as the lhs of an
  assignment, in a boolean expression, a bitvector expression, as a key in a
  table.) The only bound variables are the action data in tables. Formally:
  \[\begin{array}{l >{\triangleq}cl}
  \efvs :: \BVExpr \to \mathcal{P}(\Var) \\
  \efvs(v) && \{\} \\
  \efvs(x) && \{x\}\\
  \efvs(e_1 \binop e_2) && \efvs(e_1) \cup \efvs(e_2)\\
  \efvs(\unop e) && \efvs(unop) \\[1em]
  \bfvs :: \BExpr \to \mathcal{P}(\Var) \\
  \bfvs(\FALSE) && \{\}\\
  \bfvs(b_1 \Rightarrow b_2) && \bfvs(b_1) \cup \bfvs(b_2)\\
  \bfvs(e_1 = e_2) && \efvs(e_1) = \efvs(e_2) \\[1em]
  \fvs :: \Cmd \to \mathcal{P}(\Var) \\
  \fvs(x := e) && \{x\} \cup \fvs(e)\\
  \fvs(\havoc x) && \{x\}\\
  \fvs(\assume b) && \fvs(b)\\
  \fvs(\assert b) && \fvs(b) \\
  \fvs(c_1;c_2) && \fvs(c_1) \cup \fvs(c_1) \\
  \fvs(c_1 \choice c_2) && \fvs(c_1) \cup \fvs(c_2) \\
  \fvs(t.\apply()) &&
  t.\keys \cup \bigcup_{\lambda \vec x. c \in t.\actions} (\fvs(c) \setminus \{x_1,\ldots, x_n\})
  \end{array}\]
\end{definition}

@@

\begin{lemma}[Subset Packet Projection]
  \label{lem:subset-pkt-proj}
 Let $\pkt_1,\pkt_2 \in \Pkt$ and $U \subseteq V \subseteq \Var$,
  If $\pkt_1 =_V \pkt_2$, then $\pkt_1 =_U \pkt_2$.
\end{lemma}
\begin{proof}
  Let $\pkt_1$,$\pkt_2$, $U$, $V$ be given as above. Assume $\pkt_1 =_V \pkt_2$.
  Let $x \in U$, show that $\pkt_1(x) = \pkt_2(x)$. Since $U \subseteq V$, $x
  \in V$, so by assumption $\pkt_1(x) = \pkt_2(x)$.
\end{proof}

\begin{lemma}[Subset Projection Subset]
  \label{lem:subset-proj-subset}
  For $P,Q \subseteq \Pkt$ and $U \subseteq V \subseteq \Var$,
  If $P \subseteq_V Q$, then $P \subseteq_U Q$.
\end{lemma}

\begin{proof}
  Let $P$,$Q$,$U$,$V$ be given as above. Assume $P \subseteq_V Q$. Show $P
  \subseteq_U Q$. Let $\pkt \in P$. Since $P \subseteq_V Q$, we know that there
  is some $\pkt' \in Q$ such that $\pkt =_V \pkt'$. By Lemma~\ref{lem:subset-pkt-proj},
  $\pkt =_U \pkt'$. The result follows.
\end{proof}

\begin{corollary}[Subset Implies Projected Subset]
  \label{lem:subset-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P \subseteq Q$ then $P \subseteq_V Q$.
\end{corollary}

\begin{lemma}[Subset Projection Equality]
  \label{lem:subset-proj-equal}
  For $P,Q \subseteq \Pkt$ and $U \subseteq V \subseteq \Var$,
  If $P =_V Q$, then $P =_U Q$.
\end{lemma}

\begin{proof}
  Let $P$,$Q$,$U$,$V$ be given as above. Assume $P =_V Q$. Show $P =_U Q$. Let
  $\pkt \in P$. Since $P =_V Q$, we know that $P \subseteq_V Q$ and $Q
  \subseteq_V P$. By Lemma~\ref{lem:subset-proj-subset},$P \subseteq_U Q$ and $Q
  \subseteq_U P$. Conclude $P =_U Q$.
\end{proof}

\begin{corollary}[Equality Implies Projected Equality]
  \label{lem:equal-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$, If $P = Q$ then $P =_V Q$.
\end{corollary}

\begin{lemma}[Union Packet Projection]
  \label{lem:union-pkt-proj}
  For $\pkt_1,\pkt_2 \in \Pkt$, and $U, V \subseteq \Pkt$, if $\pkt_1 =_U
  \pkt_2$ and $\pkt_1 =_V \pkt_2$, then $\pkt_1 =_{U \cup V} \pkt_2$.
\end{lemma}

\begin{proof}
  Let $\pkt_1$, $\pkt_2$, $U$, $V$ be given as above. Assume $\pkt_1 =_U \pkt_2$
  and $\pkt_1 =_V \pkt_2$. Let $x \in U \cup V$. There are two cases. If $x \in
  U$, the assumption $\pkt_1 =_U \pkt_2 $ gives $\pkt_1(x) = \pkt_2(x)$.
  Conversely if $x \in V$, the assumption $\pkt_1 =_V \pkt_2$ gives $\pkt_1(x) =
  \pkt_2(x)$. Conclude $\pkt_1 =_{U \cup V} \pkt_2$.
\end{proof}

\begin{lemma}[Expression Projection]
  \label{lem:proj-expr}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  expression $e \in \BVExpr$, such that $\efvs(e) \subseteq V$, $\edenote{e}\pkt =
  \edenote{e}(\pkt|_V)$.
\end{lemma}
\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $e$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($e = v$)] Let $\pkt$ be given. $\edenote{v}\pkt = v = \edenote{v}{\pkt|_V}$
  \item[($e = x$)] Let $\pkt$ be given. Note that $\efvs(x) = \{x\} \subseteq V$. Compute:
    \[\begin{array}{ll}
    \edenote{x}(\pkt|_V) \\
    = (\pkt|_V)(x)
    & \text{by definition of }\edenote\cdot\\
    = \{y \mapsto \pkt(y) \mid y \in V\}(x)
    & \text{by definition of }(\cdot)|_V : \Pkt \to \Pkt\\
    = \pkt(x) & \text{since } x \in V
    \end{array}
    \]
  \item[($e = e_1 \binop e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{e_1 \binop e_2}\pkt \\
    = \edenote{e_1}\pkt \binop \edenote{e_2}\pkt & \text{definition of }\edenote\cdot \\
    = \edenote{e_1}(\pkt|_V) \binop \edenote{e_2}(\pkt|_V) & \text{by IHS since }\efvs(e_i) \subseteq \efvs(e_1 \binop e_2) \subseteq V, i = 1,2 \\
    = \edenote{e_1 \binop e_2}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \item[($e = \unop e$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{\unop e}\pkt \\
    = \unop \edenote{e}\pkt & \text{definition of }\edenote\cdot \\
    = \unop \edenote{e}(\pkt|_V) & \text{by IH, since } \efvs(e) = \efvs(\unop e) \subseteq V \\
    = \edenote{\unop e}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \end{enumerate}
\end{proof}

@@

\begin{lemma}[Input-Congruence]
  \label{lem:input-congruence}
  For $c,c',c_0 \in \Cmd$,
  if for all $\sigma \in \State$ and $\pkt \in \Pkt$, $\denote{c}^\sigma \pkt = \denote{c'}^\sigma \pkt$,
  then for all $\sigma \in \State$ and $\pkt \in \Pkt$, $\denote{c_0;c}^\sigma \pkt = \denote{c_0;c'}^\sigma\pkt$.
\end{lemma}
\begin{proof}
  Let $c$, $c'$, $c_0$, $\sigma$ and $\pkt$ be given as above.
  Let $\pkt_0 \in \denote{c_0}^\sigma \pkt$. By assumption $\denote{c}^\sigma \pkt_0 = \denote{c'}^\sigma \pkt_0$.
  Conclude ${\denote{c}^\sigma}^\dagger\left(\denote{c_0}^\sigma\pkt\right) = {\denote{c'}^\sigma}^\dagger\left(\denote{c_0}^\sigma\pkt\right)$. The result follows

\begin{lemma}[Congruence]
  \label{lem:congruence}
  For $c,c',c_a,c_b \in \Cmd$,
  if for all $\sigma \in \State$ and $\pkt \in \Pkt$, $\denote{c}^\sigma \pkt = \denote{c'}^\sigma \pkt$,
  then for all $\sigma \in \State$ and $\pkt \in \Pkt$, $\denote{c_a;c;c_b}^\sigma \pkt = \denote{c_a;c';c_b}^\sigma\pkt$.
\end{lemma}

\begin{proof}
  Let $\sigma \in \State$ and $\pkt \in \Pkt$ be arbitrary. Compute:
  \[\begin{array}{ll}
  \denote{c_a;c;c_b}^\sigma \pkt \\
  = {\denote{c_b}^\sigma}^\dagger\left({\denote{c}^\sigma}^\dagger\left(\denote{c_a}^\sigma \pkt\right)\right)\\
  = {\denote{c_b}^\sigma}^\dagger\left({\denote{c'}^\sigma}^\dagger\left(\denote{c_a}^\sigma \pkt\right)\right)
  & \text{By Lemma~\ref{lem:input-congruence}}\\
  =\denote{c_a;c;c_b}^\sigma \pkt \\
  \end{array}\]
\end{proof}

\begin{remark}
  The proofs that follow rely so heavily on Lemma~\ref{lem:congruence}, that we omit recording it's use for simplicity.
\end{remark}

@@

\begin{lemma}[Pseudo-Parametricity]
  \label{lem:parametricity}
  For $c \in \Cmd$, $\sigma \in \State$, $y \in \Var$, $\pkt \in \Pkt$, if $y
  \not\in \fvs(c)$, then $\forall \pkt' \in \denote{c}^\sigma \pkt$, $\pkt'(y) =
  \pkt(y)$.
\end{lemma}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $\{v_1,v_2\} \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:param-noninter}.
\end{proof}

\begin{lemma}[Disjoint Commutativity]
  \label{lem:disj-comm}
  For $c_1,c_2 \in \Cmd$, and $\sigma \in \State$ if $\fvs(c_1) \cap
  \fvs(c_2) = \emptyset$, $ \forall \pkt \in \Pkt. \denote{c_1;c_2}^\sigma\pkt =
  \denote{c_2;c_1}^\sigma \pkt$.
\end{lemma}
\begin{proof}
  Let $c_1, c_2$, $\sigma$, and $\pkt$ be given as above. Let $V = \Var
  \setminus (\fvs(c_1)\cup \fvs(c_2))$Let $P_i = \denote{c_i}^\sigma \pkt$ for
  $i = 1,2$, and $P_{ij} = { \denote{c_j}^\sigma}^\dagger P_i$ for $\{i,j\} =
  \{1,2\}$. Note that $P_{ij} = \denote{c_i;c_j}^\sigma \pkt$.

  It suffices to show, without loss of generality, for $\pkt' \in P_{12}$,
  there exists $\pkt_1 \in P_1$ and $\pkt_2 \in P_2$ such that
  \[\pkt'(x) = \begin{cases}
    \pkt_1(x),& \text{if } x \in \fvs(c_1)\\
    \pkt_2(x),& \text{if } x \in \fvs(c_2)\\
    \pkt(x), & \text{if } x \in V
  \end{cases} \]

  Let $\pkt' \in P_{12}$ be arbitrary. By definition, there exists $\pkt_1 \in
  P_1$ such that $\pkt' \in \denote{c_2}^\sigma \pkt_1$. By
  Lemma~\ref{lem:parametricity}, $\pkt'=_{\fvs(c_1)} \pkt_1$, so our first goal
  is done. Further, by Lemma~\ref{lem:parametricity}, $\pkt_1 =_{\fvs(c_2)}
  \pkt(x)$. So by Lemma~\ref{lem:param-noninter}, there is $\pkt_2 \in P_2$
  such that $\pkt'(x) =_{\fvs(c_2)} \pkt_2(x)$. Then by
  Lemma~\ref{lem:parametricity}, we know that $\pkt'(x) =_V \pkt(x)$. The result
  follows.
\end{proof}

@@

  \multicolumn{3}{l}{\state\sigma_T \in \BExpr} \\
  \state\sigma_T &\triangleq
  & \displaystyle\bigwedge_{ t \in T } \state\sigma^t
  \end{array}
  \]
  \caption{Symbolic State Encoding. Where $T \subseteq \Table$. We write
    $\state\sigma_c$ where $c \in \Cmd$ as shorthand for $\state\sigma_{\tables(c)}$.}
  \label{fig:table-instrument}
\end{figure}

\begin{lemma}[Symbolic State Distributes]
  \label{lem:sigma-distrib}
  For $\sigma : \Value \to \Row^*$, $T,T_1,T_2 \subseteq \Table$ such that $T = T_1 \subseteq T_2$,
  $\state\sigma_{T} \Leftrightarrow \state{\sigma}_{T_1}\wedge\state{\sigma}_{T_2}$
\end{lemma}

\begin{proof}
  Let $\sigma$, $T$, $T_1$, $T_2$ be given as above. Assume $T = T_1 \subseteq T_2$.
  Compute:
  \[\state\sigma_T\Leftrightarrow
  \left(\bigwedge_{t \in T} \state\sigma^t\right) \Leftrightarrow
  \left(\bigwedge_{t \in T_1 \cup T_2} \state\sigma^t\right) \Leftrightarrow
  \left(\bigwedge_{t \in T_1} \state\sigma^t \wedge \bigwedge_{t \in T_2}\state\sigma^t \right) \Leftrightarrow
  \state\sigma_{T_1} \wedge \state\sigma_{T_2}
  \]

@@

\begin{proof}
  By Lemma~\ref{lem:sigma-distrib} since $\tables(c_1;c_2) = \tables(c_1) \cup \tables(c_2)$.
\end{proof}

\begin{lemma}[Symbolic State Distributes Over Choice]
  \label{lem:sigma-distrib-choice}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1 \choice c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:sigma-distrib} since $\tables(c_1;c_2) = \tables(c_1) \cup \tables(c_2)$.
\end{proof}

\begin{samepage}
\begin{theorem}[Instrumentation Equivalence]
  \label{thm:instr-equiv}
  Given a set of variables $V \subseteq \Var$ that contains no ghost variables
  or symbolic variables. For every well-formed $c \in \Cmd$ such that $\fvs(c) \subseteq V$,
  well-formed state $\sigma : \Value \to \Row^*$, and packet $\pkt \in \Pkt$,
  where $T \supseteq \tables(c)$, $R \supseteq \{\rho_t \mid t \in T\}$, and $G \supseteq \{\gamma_t \mid t \in
  T\}$,

  \[\denote{c}^\sigma\,\pkt =_V \denote{\havoc {R \cup G}; \assume{\state\sigma}_T; c\instr}\,\pkt  \]
\end{theorem}
\end{samepage}
